Limits on constraining galaxy profiles with current and future strong gravitational lensing

### 2013-02-16 limits/ms.tex
Wrote mock data section and raytracing.

\newcommand{\Glass}{{\sc Glass}}
\newcommand{\PixeLens}{{\sc PixeLens}}
\newcommand{\Rmap}{\ensuremath{R_\mathrm{map}}}
\newcommand{\Rpix}{\ensuremath{R_\mathrm{pix}}}
\newcommand{\M}{\ensuremath{\mathscr{M}}}
\newcommand{\E}{\ensuremath{\mathscr{E}}}

@@

\section{Mock Galaxy Data}

\subsection{Four galaxies and their properties} %--------------------------------------------------------------

We consider four different triaxial galaxies, shown in \figref{test galaxies},
where we have varied the slope index of the stars and the dark matter. We
explore the cases were the stars follow either a $\gamma_\star=1$ or
$\gamma_\star=1.5$ profile and where the dark matter profile is cusped or
cored. The enclosed mass $M(a_\star)= 0.18\e{11}$ at the stellar scale
radius $a_\star=2$ kpc is fixed for all galaxies in order to resemble B1115. We
therefore place the galaxy at a redshift $z_L = 0.31$ in a cosmology with
$H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$, and $\Omega_\Lambda=0.72$.

\begin{figure}
\plotone{cmp_simulations.pdf}
\caption{
\textbf{(Left)} 
Three-dimensional density of the galaxies showing the stellar, dark matter,
and total densities with dotted, dashed, and solid lines, respectively. The
grey lines show the analytic forms from \eqnref{Dehnen profile}. 
\textbf{(Middle)} 
The radially averaged two-dimensional projected density in terms of the
critical density for lensing. At $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
\textbf{(Right)}
The enclosed projected mass.
}
\label{test galaxies}
\end{figure}

%\tabref{source data} summarizes
%each source and image system and \tabref{source time delays} lists the time
%delays.

Each galaxy was generated using the tool DEHNEN with the dark matter and stellar
densities roughly described by Dehnen profiles
%
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\alpha){(r/a)^{-\alpha}(1 + r/a)^{\alpha-4}}
\label{Dehnen profile}
\end{equation}
%
The individual parameters are shown in \tabref{Lens profile params}.

\begin{table}
\begin{tabular}{clllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
AC & 1 & 4 & 1 & $11^2$ \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
\end{tabular}
\caption{Profile parameters for the four test galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

@@

>>>>

\newcommand{\Glass}{{\sc Glass}}
\newcommand{\PixeLens}{{\sc PixeLens}}
\newcommand{\Rmap}{\ensuremath{R_\mathrm{map}}}
\newcommand{\Rpix}{\ensuremath{R_\mathrm{pix}}}
\newcommand{\M}{\ensuremath{\mathscr{M}}}
\newcommand{\E}{\ensuremath{\mathscr{E}}}
\newcommand{\eps}{\ensuremath{\varepsilon}}

@@

\subsection{Raytracing}
\Glass\ can also determine the position of images and time delays from 
particle-based simulation output given a source position $\vec\beta$. This is
used to generate the lens configurations used in the parameter study.  The
particles are first projected onto a very high resolution grid representing the
lens plane. The centers of each of the grid cells are mapped back onto the
source plane using \eqnref{lensing equation}. If the location on the source
plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
point on the image plane is accepted and further refined using a root finding
algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
Care must be taken that the grid resolution is high enough that the resulting
image position error is below the equivalent observational error. Time delays
are the calculated in order from the arrival time at each image (\eqnref{tau}).

\section{Parameter study}

\subsection{Mock galaxy data}

The four mock galaxies we consider have been designed to test our 
recovery procedure on galaxies that have steep and shallow dark matter
and stellar profiles. The enclosed mass in all cases is fixed at $M(a_\star)=
0.18\e{11}$ at the scale radius $a_\star=2$ kpc. These values were chosen to
closely resemble B1115. We therefore also place the galaxy at a redshift of
$z_L = 0.31$. Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
and $\Omega_\Lambda=0.72$.

The models were
first generated as three dimensional particle distributions with the
tool DEHNEN, where each component follows the profile
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
and where $\gamma$ is the profile index and $a$ is the scale radius. The
four combinations of profile indices are shown in \tabref{Lens profile params}.

\begin{table}
\begin{tabular}{clllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
AC & 1 & 4 & 1 & $11^2$ \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

In \figref{mock galaxies} we show the 3D radial density, 
the 2D projected density, and the 2D enclosed mass for each
galaxy. Solid lines represent the total mass, dashed lines the dark 
matter, and dotted lines the stellar mass. The projected plot has
been normalized to the critical density 
$\kappa_\mathrm{crit}\sim 1.8\e{9}$.

\begin{figure}
\plotone{cmp_simulations.pdf}
\caption{
\textbf{(Left)} 
Three-dimensional density of the galaxies showing the stellar, dark matter,
and total densities with dotted, dashed, and solid lines, respectively. The
grey lines show the analytic forms from \eqnref{Dehnen profile}. 
\textbf{(Middle)} 
The radially averaged two-dimensional projected density in terms of the
critical density for lensing. At $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$.
\textbf{(Right)}
The enclosed projected mass.
}
\label{mock galaxies}
\end{figure}

@@

\subsection{Recovery} %--------------------------------------------------------------
